```{r, echo = FALSE, message = FALSE, warning=FALSE}
source(here::here("scripts/setup.R"))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Setting the functions to local environment "English" 
Sys.setlocale("LC_TIME", "C")
```

#### **Sion bike sharing**

Our work is to forecast the number of bikes available for every 10 minutes of Wednesday, May 25th, at every stations in the city of Sion.

To do so, we first compile for each stations the number of bikes available only on Wednesdays. It will help us to gain some insights on particular trends for this day of the week.

Our analysis shows us that most of the time series are white noise, except for two stations:

- Campus Energypolis: e-bike
- Hôpital - CRR: e-bike

#### **Bietschhorn Station**

```{r message=FALSE, warning=FALSE, include=FALSE}
# Creation of time series
Bietschhorn <- as_tsibble(Bietschhorn)
Bietschhorn$weekday <- weekdays(Bietschhorn$date) # Get the weekday values
Bietschhorn$time <- as.POSIXct(Bietschhorn$date, format = "%H:%M:%S %p")
Bietschhorn$time <- as.numeric(Bietschhorn$date) #convert date values to numeric
as.numeric(Bietschhorn$time)

bietschhorn <- Bietschhorn %>% 
  mutate(minutes = time - lag(time, default = first(time))) # subtract days
bietschhorn$minutes <- as.numeric(as.character(bietschhorn$minutes))/60 # transform to minutes

# Filter the data by time difference of 10 min
bietschhorn <- bietschhorn %>% filter(minutes == 10) %>%
  select(-time) %>%
  relocate(date, .before = Bike)

# Identifying the gaps on the ts and fill them
bietschhorn.gaps <- has_gaps(bietschhorn)
bietschhorn.gaps <- scan_gaps(bietschhorn)
bietschhorn <- bietschhorn %>% 
  fill_gaps(.full = TRUE) 

# Replace NA's values as previous row 
bietschhorn_ts <- bietschhorn %>%
  fill(Bike, `E-Bike`, Capacity, weekday, minutes, name)
scan_gaps(bietschhorn_ts) # no missing values

#  convert our data frame from wide to long format.
bietschhorn <- bietschhorn_ts %>% 
  gather("Bike", "E-Bike", "Capacity", key = Types, value = Number) %>%
  relocate(Types, .before = weekday) %>%
  relocate(Number, .before = weekday)
```

```{r}
### Time series for Wednesdays - Bike ###
bietschhorn_wednesdays_bike <- bietschhorn %>% 
  filter(Types == "Bike" ) %>% 
  filter(weekday == "Wednesday") %>%
  mutate(t = row_number()) %>% 
  update_tsibble(index = t, regular = TRUE)

p1 <- bietschhorn_wednesdays_bike %>% 
  autoplot() +
  geom_vline(xintercept=c(54,198,342,486,630,774,918,1062), linetype="dotted") + #Per day
  ggtitle("Wednesdays time series - Bike - Bietschhorn") +
  labs(x = "Time [10']",
       y = "Number")

# Time series for Wednesdays - E-Bike
bietschhorn_wednesdays_ebike <- bietschhorn %>% 
  filter(Types == "E-Bike") %>% 
  filter(weekday == "Wednesday") %>%
  mutate(t = row_number()) %>% 
  update_tsibble(index = t, regular = TRUE)

p2 <- bietschhorn_wednesdays_ebike %>% 
  autoplot() +
  geom_vline(xintercept=c(54,198,342,486,630,774,918,1062), linetype="dotted") + # per day
  ggtitle("Wednesdays time series - E-Bike - Bietschhorn") +
  labs(x = "Time [10']",
       y = "Number")

p1 / p2
```


```{r}
# Is our time series stationary or not?
bietschhorn_wednesdays_bike %>% features(Number, unitroot_kpss) # No p-value < 0.05
bietschhorn_wednesdays_bike %>% features(Number, unitroot_ndiffs)

# Convert to stationary
bietschhorn_wednesdays_bike <- bietschhorn_wednesdays_bike %>% mutate(diff_number = difference(Number))
bietschhorn_wednesdays_bike %>% autoplot(diff_number)

# Is it white noise for the bike at the bietschhorn?
bietschhorn_wednesdays_bike %>% 
  ACF(diff_number, lag_max = 144) %>% 
  autoplot()

# Is our time series stationary or not?
bietschhorn_wednesdays_ebike %>% features(Number, unitroot_kpss) # No p-value < 0.05
bietschhorn_wednesdays_ebike %>% features(Number, unitroot_ndiffs) 

# Convert to stationary
bietschhorn_wednesdays_ebike <- bietschhorn_wednesdays_ebike %>% mutate(diff_number = difference(Number))
bietschhorn_wednesdays_ebike %>% autoplot(diff_number)

# Is it white noise for the bike at the bietschhorn?
bietschhorn_wednesdays_ebike %>% 
  ACF(diff_number, lag_max = 144) %>% 
  autoplot()
```


